Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-28 Article/main.tex
Updated Findings

\usepackage[backend=biber]{biblatex}
\addbibresource{Article.bib}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
	urlbordercolor=  0.2 0.8 0.72,
    pdftitle={Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains},}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\centerline{\includegraphics[scale=0.35]{merrill2.png}}

@@

Another important factor to consider is how to keep learners engaged and motivated with the instructional material. One model for motivating learners is the ARCS Model which was developed by John Keller which is frequently referenced in the aforementioned field of instructional design\cite{Kapp2012a}. It is comprised of four main elements with each focusing on designing instruction in a different way\cite{Kapp2012a}. 

@@

The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest. There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise. The next is to create curiosity within the learners through means such as role-playing or hands-on examples. The last means to keep attention is the variability which means periodically changing the method of delivery\cite{Kapp2012a}.

@@

Relevance refers to having the content be relevant to the learner and Kapp\cite{Kapp2012a} mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge.

@@

Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work\cite{Kapp2012a}. This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge. It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident\cite{Kapp2012a}.

@@

The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it\cite{Kapp2012a}. This can be accomplished by allowing learners to see how their newfound knowledge can be used, either through the use of a real-world demonstration or via some form of simulation\cite{Kapp2012a}.

@@

\begin{enumerate}

\item Literature surrounding the applicable fields was researched
\item Case studies concerning serious games was studied and similarities noted
\item Select theories that aid this process were pinpointed
\item From this research, recommendations for the knowledge domains were made
\end{enumerate}

@@

\section{Findings}
As described in the methodology, a large aspect of the findings comes from the literature review conducted. However, the literature review only provided segmented information that must still be distilled. This includes making note of what instructional theory is most pertinent to this study and breaking down the case studies. It also includes a short discussion on the initial reconsiderations from Kapp\cite{Kapp2012a} regarding the knowledge domains.

\subsection{Helpful Instructional Theories}
\subsection{Case Studies and the Similarities in Design Principles}

\begin{table}[htbp]
\caption{Design Principles Defined by Case Study}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based& Story-based & Clear and Simple Goals  \\
Reflection& Reflection& Quality of Feedback and Rewards  \\
-& Conceptual-Procedural & Structure of the Challenge  \\
-& -& Motion-based Interaction  \\
-& -& Simplicity  \\
\hline

\end{tabular}
\label{tab1}
\end{center}
\end{table}

\subsection{Initial Knowledge Domain Recommendations}

\section{Synthesis from Research}
\subsection{Recommendations per Knowledge Domain}
\subsection{Limitations and Future Research}

@@

%%------------------------------------------------------------
\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.
%%-------------------------------------------------------------------

>>>>

\usepackage[backend=biber]{biblatex}
\addbibresource{Article.bib}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
	urlbordercolor=  0.2 0.8 0.72,
    pdftitle={Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains},}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\centerline{\includegraphics[scale=0.37]{merrill2.png}}

@@

Another important factor to consider is how to keep learners engaged and motivated with the instructional material. One model for motivating learners is the ARCS Model which was developed by John Keller\cite{keller1987development} which is frequently referenced in the aforementioned field of instructional design\cite{Kapp2012a}. It is comprised of four main elements with each focusing on designing instruction in a different way\cite{Kapp2012a, keller1987development}. 

@@

The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest. There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise. The next is to create curiosity within the learners through means such as role-playing or hands-on examples. The last means to keep attention is the variability which means periodically changing the method of delivery\cite{Kapp2012a, keller1987development}.

@@

Relevance refers to having the content be relevant to the learner\cite{keller1987development} and Kapp\cite{Kapp2012a} mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge\cite{keller1987development}.

@@

Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work\cite{Kapp2012a, keller1987development}. This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge. It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident\cite{Kapp2012a, keller1987development}.

@@

The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it\cite{Kapp2012a, keller1987development}. This can be accomplished by allowing learners to see how their new-found knowledge can be used, either through the use of a real-world demonstration or via some form of simulation\cite{Kapp2012a, keller1987development}.

@@

\begin{enumerate}
\item Literature surrounding the applicable fields was researched
\item Case studies concerning serious games was studied and similarities noted
\item Select theories that aid this process were pinpointed
\item From this research, recommendations for the knowledge domains were made
\end{enumerate}

@@

\section{Findings}
As described in the methodology, a large aspect of the findings comes from the literature review conducted. However, the literature review only provided segmented information that must still be distilled. This includes making note of what instructional theory is most pertinent to this study and breaking down the case studies. It also includes a short discussion on the initial recommendations from Kapp\cite{Kapp2012a} regarding the knowledge domains.

\subsection{Helpful Instructional Theories}
This study detailed the ARCS model of motivation and Merrill's First Principles. While there are certainly others that would be helpful, these two provide sufficient knowledge to begin answering the question at hand. 
\\\\
Merrill's First Principles\cite{Merrill2002} provides a basis to begin development on a framework for serious games as it is already rooted in teaching. As such, using this theory in conjunction with the information gained from the case studies and the work done by Kapp\cite{Kapp2012a} it allows for a particular stricture to be followed.
\\\\
Similarly, the ARCS model for motivation developed by John Keller\cite{keller1987development} can be used in conjunction with Merrill's First Principles and the other findings to ensure learners are kept engaged and motivated with the games.

\subsection{Initial Knowledge Domain Recommendations}
Kapp\cite{Kapp2012a}, in addition to providing definitions of the various knowledge domains, provides some ways that each domain can be taught to best relay that particular type of knowledge. While these reconsiderations are derived under a gamification perspective, that can just as easily be applied for a digital game.

\begin{itemize}
\item
Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge\cite{Kapp2012a}.
\item
Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic\cite{Kapp2012a}.
\item
A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain\cite{Kapp2012a}.
\item
Procedural knowledge is best taught through having the learners work through the procedure itself in some means\cite{Kapp2012a}.
\item
Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios\cite{Kapp2012a}.
\item
Immersing the learner within a phenomena found in the affective knowledge domain is a neffective means of teaching them about it\cite{Kapp2012a}.
\item
Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in this domain.
\end{itemize}

\subsection{Case Studies and the Similarities in Design Principles}
Several case studies were examined in which some form of gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process. There are three main case studies that will be focused on in this study\cite{Dincelli2020,Sheng2007,allers2021children}.
\\\\
The first of these is titled, \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"} and focused on developing a gamified system to teach employees about security issues - focussing on social media and social engineering\cite{Dincelli2020}. 
\\\\
The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing that is done through the use of fake websites and the ways links are used for this\cite{Sheng2007}. 
\\\\
The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}
\begin{table}[htbp]
\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
\begin{adjustwidth}{-0.6cm}{}
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based	& Story-based 			& Clear and Simple Goals  \\
Reflection	& Reflection			& Quality of Feedback and Rewards  \\
	-		& Conceptual-Procedural & Structure of the Challenge  \\
	-		& 		-				& Motion-based Interaction  \\
	-		& 		-				& Simplicity  \\
\hline

\end{tabular}
\label{tab1}
\end{adjustwidth}
\end{table}

\section{Synthesis from Research}
\subsection{Recommendations per Knowledge Domain}

\section{Limitations and Future Research}

@@
